%%# -*- coding:utf-8 -*-

\documentclass[fontset=windows]{article}
% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2022


% ready for submission
% \usepackage{neurips_2022}


% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2022}

\PassOptionsToPackage{numbers, compress}{natbib}  % ref https://arxiv.org/abs/2209.09407
% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[final]{neurips_2022}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2022}

\usepackage[UTF8]{ctex}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{graphicx}       %%  图片包
\usepackage{subfig}
\usepackage{geometry}
\usepackage{calligra}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{multirow}
\usepackage{diagbox}
\usepackage{hyperref}
\usepackage{tablefootnote}
\usepackage{indentfirst}
\setlength{\parindent}{2em}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{notations}{Notations}

\title{音视频编码技术期末报告 -- 多类图像去雾复现}


% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.


\author{%
    刘昭炀\\ %\thanks{Use footnote for providing further information
    电子与信息工程学院\quad 信息与通信工程专业\\
    22215608\\
    \href{mailto:liuzhy86@mail2.sysu.edu.cn}{liuzhy86@mail2.sysu.edu.cn}\\
}


\begin{document}
{

\maketitle

\begin{abstract}
    \indent 由于大气颗粒对光的散射，在恶劣天气（例如阴霾、雾、薄雾、烟雾）下拍摄的图像的颜色，对比度发生变化、能见度降低，图像信息发生了不可逆的变化。这些退化不仅会影响图像的视觉质量；更重要的是它们会改变图像中所包含的重要信息内容，进而降低一些室外视觉系统以及一些计算机视觉算法的性能。所以恶劣天气条件下的图像增强、图像复原有着切实的应用价值。单图像去雾（single image dehazing，SID）方法用于从单个模糊图像恢复可见性。由于其病态性质，SID 是一个具有挑战性的问题。通常，大气散射模型（atmospheric scattering model，ATSM）用于解决SID问题。传输和介质透射率（大气光）是ATSM的两个主要参数，基于大气散射物理模型的SID算法聚焦于如何更好地估计这两个参数，以获取更好的图像复原效果。

    \indent 本文主要复现了几种基于大气散射物理模型的传统方法去雾算法，它们各自拥有不同的优势（速度、成像效果），流程大同小异。在本文最后，对比了不同算法的效果。本文复现的源码可见于Github。\footnote{源代码可见于：\url{https://github.com/AnnLIU15/img_process/tree/SID}}
\end{abstract}

% footnote ref: https://arxiv.org/pdf/2108.10026.pdf
\begingroup
\let\clearpage\relax
\include{sec/sec1.tex}%\section*{References}

\include{sec/sec2.tex}
\include{sec/sec3.tex}
\include{sec/sec4.tex}
\include{sec/sec5.tex}
\endgroup

\medskip
{\small{}\bibliographystyle{unsrt}
\bibliography{report}
}{\small\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



% \appendix


% \section{Appendix}
% \textit{proof} Theorem~\ref{thm31}

\end{document}